\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-03-15 write_up/mixfishsim_ecolmod.tex
Update to plots
Updated figure

We allow the simulation to run unrestricted for 5 years, and subsequently close
areas for the last 5 years of the simulation based on data (either derived from
the commercial catches, fisheries-independent survey or the 'real population')
used at different spatial and temporal scales.

@@

i. Extract data source
ii. Aggregate according to resolution
iii. Interpolate across entire area at desired resoltion
iv. Close top 5 \% of areas

\begin{table}[!ht]
\caption{Closure scenarios}
\begin{tabular}{ p{4cm } p{4cm} p{4cm}}
	\hline
	Data type & Temporal resolution & Spatial resolution \\
	\hline
	Commercial logs, survey data, real population & weekly, monthly, years
	& 1, 2, 5, 10 \\ 
\end{tabular}
\label{tab:x}
\end{table}

ABOVE WOULD BE BETTER AS SOME SORT OF GRAPHICAL ILLUSTRATION OF AGGREGATION
CONSEQUENCES, E.G. 
COMMERCIAL DATA SPARSITY, SURVEY DATA CONSISTENCY, REAL
POPULATION IS ALL.

TEMPORALLY VARYING PROPORTIONS DIVIDED BY WEEK, MONTH, YEAR

CELLS AGGREGATED ACCORDING TO SIMULATION EXAMPLES !!!

Total 56 scenarios.

@@

>>>>

We allow the simulation to run unrestricted for 5 years, and subsequently close
areas for the last 5 years of the simulation based on data (either derived from
the commercial catches, fisheries-independent survey or the 'real population')
used at different spatial and temporal scales. \\

@@

\begin{enumerate}
	\item Extract data source
	\item Aggregate according to resolution
	\item Interpolate across entire area at desired resoltion
	\item Close top 5 \% of areas
\end{enumerate}

In total 56 closure scenarios were run which represent combinations of: three
data types; commercial logbook data, survey data and 'real population', three
temporal resolutions; weekly, monthly and yearly closures, and four spatial
resolutions; 1 x 1 grid, 5 x 5 grid, 10 x 10 grid and 20 x 20 grid. Survey
closures were on an annual basis, as the most temporally resolved survey data
available.

@@

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
	\caption{Data aggregation at different spatial resolutions}
	\label{fig:0a}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
	\caption{Data aggregation at different temporal resolutions}
	\label{fig:0b}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/Overview_plot_highPop}
	\caption{Comparison of closure scenarios}
	\label{fig:0c}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trends}
	\caption{Comparison of closure scenarios - F trends}
	\label{fig:0d}
\end{figure}

// 
//Supplementary
//
